### 2023-10-17 main.tex
bozza 1

This is a new configuration at site $x$ where, if $x\in\{q_{1},\ldots,q_{i}\}$, the occupation $\tau_{x}$ is replaced by $N$, while it is left uncaged if $x\notin \{q_{1},\ldots,q_{i}\}$. The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation. By considering a fixed $\langle\bm{\tau}|$, and by using \eqref{goodTP-S2} we obtain 

@@

@@

@@

	Proposal

@@

For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, by using equation \eqref{ResulsBasis},we obtain 

@@

	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{y}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}

@@

To compute correlations it is enough the above expression, however using \eqref{ABS} it is possible to write $\Psi(\bm{\tau})$ explicitly, see Appendix \ref{appB}.\\

@@

	+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1

@@

thus we have that it is enough to prove that

@@

	+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&0
We now consider the second term of the above expression. For any fixed $\ell$ and for any fixed $\bm{\tau}\in \Omega_{\ell}$, $b$ empty occupations are replaced by all possible non-empty species. For a fixed $b$, if the configuration $\bm{\tau}\in \Omega_{\ell}$ with has $\ell<b$, then the this term do not produce any contribution. On the other hand, if $b\geq \ell$ we obtain from $\bm{\tau}$ all possible configuration in the space $ \Omega_{\ell-b}$. Each of such a configuration is counted $\binom{L-\ell+b}{b}$. By calling $r=\ell-b$ if $b\leq \ell$ we have that 

@@

	\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=& \sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\\+&\sum_{b=1}^{L-m}(-1)^{b}\sum_{r=0}^{L-m-b}\binom{L-m-r}{b}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})

@@

\sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\sum_{\ell=1}^{L-m-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-m-\ell}{b}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
Using the Binomial theorem, for every $\ell\in \{0,\ldots, L-m-b\}$, we have that

@@

 \Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt

@@

The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
\begin{equation}
	|\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
\end{equation}
where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$
\begin{equation}
	\begin{split}
		\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
		\\&+
		\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right) 
		\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}
		\\&
		\sum_{c_{1}=0}^{1-\delta_{\eta_{1}^{b},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L}^{b},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\eta_{y}^{b}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}^{b}}^{(1-c_{y})(1-\delta_{\eta_{y},N})}
	\end{split}
\end{equation}
where we have introduced, $\forall x\in \{1,\ldots,L\}$
\begin{equation}\label{eta-notation}
	\eta_{x}^{b}(q_{1},\ldots,q_{b})=\begin{cases}
		\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
		i_{q_{k}}\qquad &\text{if}\quad x=q_{k}\quad \text{with}\quad q_{k}\in\{q_{1},\ldots,q_{b}\}
	\end{cases}%\qquad \theta_{x}=\begin{cases}
		%\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
		%	1 \qquad &\text{otherwise}
		%\end{cases}
	\end{equation}
	The dependence of $\eta_{x}^{b}$ with respect to $(q_{1},\ldots,q_{b})$ is usually understood for the sake of notation. 
\begin{comment}
	{\color{blue}
		\begin{equation}\label{steadyStateH-coeff}
			\begin{split}
				\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
				\\&+
				\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{s=1}^{b}\delta_{s_{q_{r}},N}\right) 
				\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
				\\&
				\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
				\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
				\\ &
				\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
				\prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
			\end{split}
		\end{equation}
	}
\end{comment}
\newline \newline
	\textbf{Remark}: we observe that if no holes are present, i.e. if $\tau_{x}\neq N$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
	\begin{equation}\label{LinkABS-corr}
		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
	\end{equation}
	When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.

>>>>

This is a new configuration at site $x$ where, if $x\in\{q_{1},\ldots,q_{i}\}$, the occupation $\tau_{x}$ is replaced by $N$, while it is left uncaged if $x\notin \{q_{1},\ldots,q_{i}\}$. The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation. } \\ By considering a fixed $\langle\bm{\tau}|$, and by using \eqref{goodTP-S2} we obtain 

@@

where, for arbitrary $i\in\{1,\ldots,L\}$,  $\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{i}}\ldots,\tau_{L})$ means that the $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ have been replaced by $N$. \\
	Old proposal

@@

\end{equation*}}

@@

@@

For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, by using equation \eqref{ResulsBasis}, we obtain 

@@

	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}

@@

To compute correlations it is enough the above expression. Using \eqref{ABS} it is possible to write $\Psi(\bm{\tau})$ explicitly. We report this explicit formula and the proof in Appendix \ref{appB}.\\
The expression \eqref{SteadyState-coeff-implicit} has two contribution. First a term $\Psi^{'}(\bm{\tau})$ and second a where $b$ of the empty occupations of $\bm{\tau}$ have been replaced by all possible species from $1$ to $N-1$. If the configuration $\bm{\tau}$ has no empty species, this second term vanishes. The existence of the second term is motivated by the fact that, the empty occupation at each site $x$ depend on the other species via $1=\sum_{a=1}^{N}n_{a}^{x}$.\\  

@@

	+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=1

@@

thus, it is enough to prove that

@@

	+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=0
We now consider the second term of the above expression. For any fixed $\ell$ and for any fixed $\bm{\tau}\in \Omega_{\ell}$, $b$ empty occupations are replaced by all possible non-empty species. For a fixed $b$, if the configuration $\bm{\tau}\in \Omega_{\ell}$ with has $\ell<b$, then the this term do not produce any contribution. On the other hand, if $b\geq \ell$ we obtain from $\bm{\tau}$ all possible configuration in the space $ \Omega_{\ell-b}$, where $b$ empties have been replaced by all  species from $1$ to $N-1$. Each of such a configuration is counted $\binom{L-\ell+b}{b}$. By calling $r=\ell-b$ if $b\leq \ell$ we have that 

@@

	\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=& \sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\nonumber
	\\+&\sum_{b=1}^{L-m}(-1)^{b}\sum_{r=0}^{L-m-b}\binom{L-m-r}{b}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})

@@

\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=&\sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\nonumber
\\+&\sum_{\ell=1}^{L-m-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-m-\ell}{b}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
Using the Binomial theorem, for every $\ell\in \{0,\ldots, L-m-1\}$, we have that

@@

 \Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt

@@

The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
\begin{equation}
	|\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
\end{equation}
where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$
\begin{equation}
	\begin{split}
		\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
		\\&+
		\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right) 
		\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}
		\\&
		\sum_{c_{1}=0}^{1-\delta_{\eta_{1}^{b},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L}^{b},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\eta_{y}^{b}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}^{b}}^{(1-c_{y})(1-\delta_{\eta_{y},N})}
	\end{split}
\end{equation}
where we have introduced, $\forall x\in \{1,\ldots,L\}$
\begin{equation}\label{eta-notation}
	\eta_{x}^{b}(q_{1},\ldots,q_{b})=\begin{cases}
		\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
		i_{q_{k}}\qquad &\text{if}\quad x=q_{k}\quad \text{with}\quad q_{k}\in\{q_{1},\ldots,q_{b}\}
	\end{cases}%\qquad \theta_{x}=\begin{cases}
		%\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
		%	1 \qquad &\text{otherwise}
		%\end{cases}
	\end{equation}
	The dependence of $\eta_{x}^{b}$ with respect to $(q_{1},\ldots,q_{b})$ is usually understood for the sake of notation. 
\begin{comment}
	{\color{blue}
		\begin{equation}\label{steadyStateH-coeff}
			\begin{split}
				\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
				\\&+
				\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{s=1}^{b}\delta_{s_{q_{r}},N}\right) 
				\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
				\\&
				\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
				\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
				\\ &
				\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
				\prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
			\end{split}
		\end{equation}
	}
\end{comment}
%	\textbf{Remark}: we observe that if no holes are present, i.e. if $\tau_{x}\neq N$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
%	\begin{equation}\label{LinkABS-corr}
%		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
%	\end{equation}
%	When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.
